Learning Causally-Generated Stationary Time Series

### 2017-02-22 doc/paper.tex
Added missing image
Bit of discussion

\begin{figure*}[t]
    % \vskip 0.2in
    \centering
    \includegraphics[width=\linewidth]{../../GGPCM/output/interpolation2.pdf}
    \caption{Generative process of the CGPCM. Shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$.}
    \label{fig:interpolation}
    % \vskip -0.2in
\end{figure*}

@@

\subsection{Fricative Consonant}
{\color{red} Experiment.}

\subsection{Head-Related Transfer Function}
{\color{red} Experiment.}

\section{Discussion}
\begin{itemize}
    \item Discussion from \cite{Tobar:2015:Learning_Stationary,Tobar:2015:Inter-Domain_Inducing}
    \item Improved interdomain transformation
    \item HCM to improve sampling
    \item Bayesian inference over the parameters
    \item Improved model solving
\end{itemize}

>>>>

\begin{figure*}[t]
    % \vskip 0.2in
    \centering
    \includegraphics[width=\linewidth]{resources/interpolation.pdf}
    \caption{Generative process of the CGPCM. Shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$.}
    \label{fig:interpolation}
    % \vskip -0.2in
\end{figure*}

@@

\subsection{Unvoiced Fricatives}
Unvoiced fricatives are consonants produced by forcing air through a narrow constriction in the vocal tract, thereby creating a noisy, turbulant sound \cite{Taylor:2009:Text-To-Speech_Synthesis}.

\subsection{Head-Related Transfer Function}
A head-related transfer function (HRTF) is a transfer function that describes how an ear receives sound from a certain point in space.

\section{Discussion}
We have presented the CGPCM as a model for causally-generated stationary time series. Inference is performed by finding an initial approximation through a variational mean-field approach, and then refining this approximation through a variational structured mean-field approach combined with elliptical slice sampling. The GPCM has been validated {\color{red} discussion of results of experiments here.}

In future research on the CGPCM, various directions can be explored: First, the model could be extented to multidimensional input and output spaces by following a construction similar to that by \citet{Bruinsma:2016:GGPCM}. Second, the application of more efficient sparse approximation for $h$ and $x$, such as the tree-structured approximation \cite{Bui:2014:Tree-Structured_Gaussian}, would scale the CGPCM to larger data sets. Third, to deal with signals that are band-limited, but not necessarily baseband, the use of an harmonic interdomain transformation \cite{Tobar:2015:Inter-Domain_Inducing} and an harmonic extension of the causal interdomain transformation could be explored. Fourth, in the low noise case, ESS has a hard time exploring $q(u)$; therefore, in that case, afternative sampling algorithms such as Hamiltonian Monte-Carlo \cite{Neal:2012:MCMC_Using_Hamiltonian_Dynamics} could be used. Finally, using an approach similar to that by \citet{Lazaro-Gredilla:2013:Variational_Inference_for_Mahalanobis_Distance}, Bayesian inference in the hyperparameters could be attempted.
